---
title: "Descriptive Statistics"
author: "Morgane Soufflet"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data
```{r libraries, echo=FALSE}

library(tidyverse)
library(sf)
library(dplyr)
library(patchwork)
#Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```

```{r data, echo=FALSE}
dep_carte = st_read("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/DEPARTEMENTS_1876.shp", options = "ENCODING=UTF-8")
data <- read.csv("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Data/Output/merged_elections.csv")
```


# Phylloxera Descriptive Statistics 
### Phylloxera contamination
```{r map, echo=FALSE, fig.width=14, fig.height=20}
# FIRST YEAR OF CONTAMINATION
map_data_first <- data %>% 
  filter(first_year != 0) %>%
  group_by(nomdepancien) %>%
  summarise(first_year = min(first_year, na.rm = TRUE))

# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data_first, by = c("dep_name" = "nomdepancien"))

  # Map first_year
p <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = first_year)) +
        scale_fill_viridis_c(option = "rocket", direction =1, name = "First year of contamination",
                            breaks = seq(1863, 1888, by =2),
                            labels = seq(1863, 1888, by =2)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9),
        legend.key.size = unit(1, "cm")) +
        labs(title = "First year of Phylloxera contamination by department")

#print(p)

ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_firstyear.png", 
       plot = p, width = 10, height = 8)

# TOTAL CONTAMINATION
map_data_first <- data %>% 
  group_by(nomdepancien) %>%
  mutate(last_year = min(an[phyllox_tot == 1], na.rm = TRUE)) %>% 
  filter(!is.infinite(last_year)) %>% # removes never contaminated
  summarise(last_year = first(last_year)) 

# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data_first, by = c("dep_name" = "nomdepancien"))

  # Map first_year
p2 <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = last_year)) +
        scale_fill_viridis_c(option = "rocket", direction =1, name = "Year of total contamination",
                            breaks = seq(1875, 1890, by =2),
                            labels = seq(1875, 1890, by =2)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 20),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9),
        legend.key.size = unit(1, "cm")) +
        labs(title = "Year of total contamination by department")

#print(p2)
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_totalconta.png", 
       plot = p2, width = 10, height = 8)

(p / p2) + 
  plot_annotation(theme = theme(plot.title = element_text(size = 18)))
```


### Contamination after the first election
```{r map_before_1876, echo=FALSE}
map_data_first <- data %>% 
  filter(first_year != 0) %>%
  filter(first_year > 1875) %>%
  group_by(nomdepancien) %>%
  summarise(first_year = min(first_year, na.rm = TRUE))

# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data_first, by = c("dep_name" = "nomdepancien"))

  # Map first_year
p <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = first_year)) +
        scale_fill_viridis_c(option = "rocket", direction =1, name = "First year of contamination",
                            breaks = seq(1876, 1888, by =1),
                            labels = seq(1876, 1888, by =1)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 14),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.8, "cm")) #+
        #labs(title = "First Year of Phylloxera Contamination by Department")

print(p)
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_firstyear_1876.png", 
       plot = p, width = 10, height = 8)
```

```{r map_beforeafter_1876, echo=FALSE}
map_data_first <- data %>% 
  filter(first_year != 0) %>%
  group_by(nomdepancien) %>%
  summarise(first_year = min(first_year, na.rm = TRUE)) %>%
  mutate(period = case_when(
    first_year < 1876 ~ "Before 1876",
    first_year > 1875 ~ "After 1875"  # everything else (never contaminated)
  ))

# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data_first, by = c("dep_name" = "nomdepancien"))

  # Map first_year
p <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = period)) +
        scale_fill_viridis_d(option = "rocket", direction = -1, 
                     name = "First year of contamination") +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 14),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.8, "cm")) #+
        #labs(title = "First Year of Phylloxera Contamination by Department")

print(p)
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_firstyear_1876.png", 
       plot = p, width = 10, height = 8)
```

### Year of total contamination per departments
```{r maptot_beforeafter_1876, echo=FALSE}

map_data_first <- data %>% 
  group_by(nomdepancien) %>%
  mutate(last_year = min(an[phyllox_tot == 1], na.rm = TRUE)) %>% 
  filter(!is.infinite(last_year)) %>% # removes never contaminated
  summarise(last_year = first(last_year)) %>% 
  mutate(period = case_when(
    last_year < 1876 ~ "Before 1876",
    last_year > 1875 ~ "After 1875"  
  ))

# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data_first, by = c("dep_name" = "nomdepancien"))

  # Map first_year
p <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = period)) +
        scale_fill_viridis_d(option = "rocket", direction = -1, 
                     name = "Year of full contamination") +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 14),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.8, "cm")) #+
        #labs(title = "First Year of Phylloxera Contamination by Department")

print(p)
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_firstyear_1876_tot.png", 
       plot = p, width = 10, height = 8)
```

### Number of Contaminated Years per Department
```{r contamination, echo=FALSE}
map_data_nb <- data %>% 
  group_by(nomdepancien) %>%
  summarise(nb_conta = max(nb_conta,na.rm = TRUE))

# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data_nb, by = c("dep_name" = "nomdepancien"))

pc <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = nb_conta)) +
        scale_fill_viridis_c(option = "rocket", direction =-1, name = "Number contaminated of years",
                            breaks = seq(0, 26, by =5)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 14)) #+
        #labs(title = "Number of years contaminated by Department")

#print(pc)
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_nb_conta.png", 
       plot = pc, width = 10, height = 8)

```

### Cumulative percentage of Departments contaminated by Phylloxera over the years
```{r linegraph, echo=FALSE}
# Cumulative nb of contaminated dep over time

dep_cum <- data %>%
  filter(an > 1861 & an < 1892) %>%
  group_by(an) %>%
  summarise(contaminated = sum(galet, na.rm = TRUE)) %>% 
  arrange(an) %>%
  mutate(cumulative_perc = cummax(contaminated)/85*100)

p_cumul <- ggplot(dep_cum, aes(x = an, y = cumulative_perc)) +
  geom_line(color = "#d73027", linewidth = 1) +
  geom_point(color = "#d73027", size = 2) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 14)) +
  labs(x = "year",
      y = "Percentage of departments contaminated") +
  scale_x_continuous(breaks = seq(1860, 1891, by = 2))

print(p_cumul)

ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/cum_year_conta_dep.png",
       plot = p_cumul, width = 10, height = 8)

```

## Wine production
```{r wine_prod, echo=FALSE, fig.width=14, fig.height=20}
# MAP WINE 1860
map_data_1860 <- data %>% 
  filter(an == 1860) %>%
  group_by(nomdepancien)
    
# Join shapefile with data
dep_carte_merged_1860 <- dep_carte %>%
  left_join(map_data_1860, by = c("dep_name" = "nomdepancien"))

# Map 1876 wine prod
p1 <- ggplot(dep_carte_merged_1860) +
        geom_sf(aes(fill = logprod_vin)) +
        scale_fill_viridis_c(option = "rocket", direction =-1, name = "Log of wine production",
                            breaks = seq(3, 16, by =3),
                            labels = seq(3, 16, by =3),
                            limits = c(3,16)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust = 0.5, size = 30)) +
        labs(title = "1860")
p1 <- p1 + theme(
    plot.title = element_text(size = 12),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1, "cm")
  )
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_logprod_1860.png", 
       plot = p1, width = 10, height = 8)

###############
# MAP WINE 1876
###############
map_data_1876 <- data %>% 
  filter(an == 1876) %>%
  group_by(nomdepancien)
    
# Join shapefile with data
dep_carte_merged_1876 <- dep_carte %>%
  left_join(map_data_1876, by = c("dep_name" = "nomdepancien"))

# Map 1876 wine prod
p2 <- ggplot(dep_carte_merged_1876) +
        geom_sf(aes(fill = logprod_vin)) +
        scale_fill_viridis_c(option = "rocket", direction =-1, name = "Log of wine production",
                            breaks = seq(3, 16, by =3),
                            labels = seq(3, 16, by =3),
                            limits = c(3,16)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust =0.5, size = 30)) +
        labs(title = "1876")

p2 <- p2 + theme(
    plot.title = element_text(size = 12),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1, "cm")
  )

ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_logprod_1876.png", 
       plot = p2, width = 10, height = 8)


# MAP WINE 1890
map_data_1890 <- data %>% 
  filter(an == 1890) %>%
  group_by(nomdepancien)
    
# Join shapefile with data
dep_carte_merged_1890 <- dep_carte %>%
  left_join(map_data_1890, by = c("dep_name" = "nomdepancien"))

# Map 1890 wine prod
p3 <- ggplot(dep_carte_merged_1890) +
        geom_sf(aes(fill = logprod_vin)) +
        scale_fill_viridis_c(option = "rocket", direction =-1, name = "Log of wine production",
                            breaks = seq(3, 16, by =3),
                            labels = seq(3, 16, by =3),
                            limits = c(3,16)) +
        theme_void() + #replaces theme_minimal() and removes the grid, axis, labels and coordinates (including the background)
        theme(plot.title = element_text(hjust =0.5, size = 30)) +
        labs(title = "1890")

p3 <- p3 + theme(
    plot.title = element_text(size = 12),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1, "cm")
  )

ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_logprod_1890.png", 
       plot = p3, width = 10, height = 8)

# MAP WINE 1905
map_data <- data %>% 
  filter(an == 1905) %>%
  group_by(nomdepancien)
    
# Join shapefile with data
dep_carte_merged <- dep_carte %>%
  left_join(map_data, by = c("dep_name" = "nomdepancien"))

# Map 1890 wine prod
p4 <- ggplot(dep_carte_merged) +
        geom_sf(aes(fill = logprod_vin)) +
        scale_fill_viridis_c(option = "rocket", direction =-1, name = "Log of wine production",
                            breaks = seq(3, 16, by =3),
                            labels = seq(3, 16, by =3),
                            limits = c(3,16)) +
        theme_void() + 
        theme(plot.title = element_text(hjust = 0.5, size = 30)) +
        labs(title = "1905")

p4 <- p4 + theme(
    plot.title = element_text(size = 12),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    legend.key.size = unit(1, "cm")
  )

ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_logprod_1905.png", 
       plot = p4, width = 10, height = 8)


(p1 | p2) / (p3 | p4) + plot_layout(guides = "collect") +
  plot_annotation(title = "Log Wine production", 
                  theme = theme(plot.title = element_text(size = 18)))
```




# Legislative Elections Descriptive Statistics
## Nuances
```{r nuance, echo=FALSE, fig.width=20, fig.height=26}
# Define the election years
years <- c(1876, 1881, 1885, 1889, 1893, 1898, 1902, 1906, 1910)

# Store plots in a list
plots <- list()

for (year in years) {

  #### MAP DOMINANT PARTIES
  map_data <- data %>% 
    filter(an == year) %>%
    select(nomdepancien, voteG, voteCG, voteC, voteCD, voteD) %>%
    mutate(major_party = case_when(
      voteG  == pmax(voteG, voteCG, voteC, voteCD, voteD, na.rm=TRUE) ~ "Left",
      voteCG == pmax(voteG, voteCG, voteC, voteCD, voteD, na.rm=TRUE) ~ "Center-Left",
      voteC  == pmax(voteG, voteCG, voteC, voteCD, voteD, na.rm=TRUE) ~ "Center",
      voteCD == pmax(voteG, voteCG, voteC, voteCD, voteD, na.rm=TRUE) ~ "Center-Right",
      voteD  == pmax(voteG, voteCG, voteC, voteCD, voteD, na.rm=TRUE) ~ "Right"
    ))
      
  # Join shapefile with data
  dep_carte_merged <- dep_carte %>%
    left_join(map_data, by = c("dep_name" = "nomdepancien"))

  # Map 1889
  p_pol <- ggplot(dep_carte_merged) +
          geom_sf(aes(fill = major_party)) +
          scale_fill_manual(values = c(
            "Left"         = "#d73027",
            "Center-Left"  = "#fc8d59",
            "Center"       = "#fee090",
            "Center-Right" = "#91bfdb",
            "Right"        = "#4575b4"
          ), 
          breaks = c("Left", "Center-Left", "Center", "Center-Right", "Right"),
          limits = c("Left", "Center-Left", "Center", "Center-Right", "Right"), #forces to show every party even if not present for one year,
          drop = FALSE, 
          name = "Dominant vote") +
          theme_void() +
          theme(plot.title = element_text(hjust = 0.5, size = 30)) +
          labs(title = year)

  #Apply themes
  p_pol <- p_pol + theme(
    plot.title = element_text(size = 10),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 19),
    legend.key.size = unit(0.9, "cm")
  )
  # Save graph
  ggsave(paste0("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_dominant_pol_nuance_", year, ".png"), 
        plot = p_pol, width = 10, height = 8)

  # Hide legend for all plots except the first year (to facilitate merging afterwards)
  if (year != years[1]) {
    p_pol <- p_pol + theme(legend.position = "none")
  }
  # Add graph to list
  plots[[as.character(year)]] <- p_pol

}

# Combine all plots
combined <- wrap_plots(plots, ncol = 2) & 
  theme(legend.position = "right")

combined <- combined + plot_layout(guides = "collect")
print(combined)

```



## PARTIES
### Dominant vote per party by departments
```{r party_1876, echo=FALSE}
# Define the election years
years <- c(1876)

for (year in years) {

  #### MAP DOMINANT PARTIES
  map_data <- data %>% 
    filter(an == year) %>%
    select(nomdepancien, voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, 
         voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE) %>%
    mutate(across(starts_with("voix"), ~as.numeric(replace(., . == "" | is.na(.), 0)))) %>%
    mutate(major_party = case_when(
      voixRAD     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Radical",
      voixREP     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Republican",
      voixREPCONS == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Republican Conservative",
      voixCONST   == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Constitutional",
      voixBON     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Bonapartist",
      voixMON     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Monarchist",
      voixLEG     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Legitimist",
      voixCENT    == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Center",
      voixDIV     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Diverse",
      voixCONS    == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Conservative",
      voixCED     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Center-Right",
      voixCLE     == pmax(voixRAD, voixREP, voixREPCONS, voixCONST, voixDIV, voixCENT, voixCED, voixBON, voixMON, voixLEG, voixCONS, voixCLE, na.rm=TRUE) ~ "Clerical"
  ))
      
  # Join shapefile with data
  dep_carte_merged <- dep_carte %>%
    left_join(map_data, by = c("dep_name" = "nomdepancien"))

  # Map
  p_pol <- ggplot(dep_carte_merged) +
          geom_sf(aes(fill = major_party)) +
          scale_fill_manual(values = c(
            # Left (1)
            "Radical"                = "#d73027",
            # Center-Left/Center (2-3)
            "Republican"             = "#f46d43",
            "Republican Conservative"= "#fdae61",
            "Constitutional"         = "#fee090",
            "Center"                 = "#ffffbf",
            "Center-Right"           = "#fff176", 
            # Unclassified (0)
            "Diverse"                = "#cccccc",
            # Center-Right (4)
            "Bonapartist"            = "#abd9e9",
            # Right (5)
            "Monarchist"             = "#4575b4",
            "Legitimist"             = "#313695",
            "Conservative"           = "#1a237e",
            "Clerical"               = "#141A61" 
          ),
          breaks = c("Radical", "Republican", "Republican Conservative", "Constitutional",
             "Center", "Center-Right", "Diverse", "Conservative", 
             "Bonapartist", "Monarchist", "Legitimist", "Clerical"),
          name = "Dominant vote", na.value = "grey80") +
          theme_void() 
          theme(plot.title = element_text(hjust = 0.5, size = 14)) +
          labs(title = year)
  print(p_pol)
  ggsave(paste0("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_dominant_pol_party_", year, ".png"), 
        plot = p_pol, width = 10, height = 8)
  #cat("Saved map for year", year, "\n")
}
```


```{r party_1889, echo=FALSE}
## 1889
map_data_1889 <- data %>%
  filter(an == 1889) %>%
  select(nomdepancien, voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP, 
         voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS, 
         voixBOUL, voixREAC, voixBON, voixMON, voixCONS) %>%
  mutate(across(-nomdepancien, ~as.numeric(replace(., is.na(.), 0)))) %>%
  mutate(major_party = case_when(
    voixSOC     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Socialist",
    voixRADSOC  == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Radical-Socialist",
    voixRAD     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Radical",
    voixRADDIV  == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Diverse Radical",
    voixREP     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Republican",
    voixOPP     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Opposition Republican",
    voixREPDIV  == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Diverse Republican",
    voixDIV     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Diverse",
    voixLIB     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Liberal",
    voixREVIS   == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Revisionist",
    voixBOUL    == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Boulangist",
    voixREAC    == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Reactionary",
    voixBON     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Bonapartist",
    voixMON     == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Monarchist",
    voixCONS    == pmax(voixSOC, voixRADSOC, voixRAD, voixRADDIV, voixREP,
                        voixOPP, voixREPDIV, voixDIV, voixLIB, voixREVIS,
                        voixBOUL, voixREAC, voixBON, voixMON, voixCONS, na.rm=TRUE) ~ "Conservative"
  ))

dep_carte_merged_1889 <- dep_carte %>%
  left_join(map_data_1889, by = c("dep_name" = "nomdepancien"))

p_1889 <- ggplot(dep_carte_merged_1889) +
  geom_sf(aes(fill = major_party)) +
  scale_fill_manual(values = c(
    # Left (1)
    "Socialist"             = "#67000d",
    "Radical-Socialist"     = "#a50026",
    "Radical"               = "#d73027",
    # Center-Left (2)
    "Diverse Radical"       = "#f46d43",
    # Center-Left/Center (2-3)
    "Republican"            = "#fdae61",
    "Opposition Republican" = "#fee090",
    # Center (3)
    "Diverse Republican"    = "#ffffbf",
    "Diverse"               = "#fff176",
    # Center-Right (4)
    "Liberal"               = "#e0f3f8",
    "Revisionist"           = "#abd9e9",
    "Boulangist"            = "#74add1",
    "Bonapartist"           = "#4575b4",
    # Right (5)
    "Monarchist"            = "#313695",
    "Conservative"          = "#1a237e",
    "Reactionary"           = "#141A61" 
  ),
  breaks = c("Socialist", "Radical-Socialist", "Radical", "Diverse Radical",
             "Republican", "Opposition Republican", "Diverse Republican",
             "Diverse", "Liberal", "Revisionist", "Boulangist",
             "Bonapartist", "Monarchist", "Conservative", "Reactionary"),
  name = "Dominant party", na.value = "grey80") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, size = 14)) +
  labs(title = "1889")

print(p_1889)
ggsave("C:/Users/morga/OneDrive/Documents/MASTER_2/Semester_2/Mémoire/Phylloxera_Crime/Stat descriptives/map_dominant_pol_party_1889.png",
       plot = p_1889, width = 10, height = 8)
```

